---
title: "Challenge B"
author: "Oriane & Stacy"
date: "28 novembre 2017"
output: html_document
---

## Task 1B

# Step 1 :

 Coucou We choose the random forest techninques blabla 

#Step 2

```{r first, include=FALSE}
library(tidyverse)
library(np)
library(readr)
library(randomForest)
train <- read_csv("~/rprog/train.csv")
```

First, we erase the column ID. 
Then, since variables are not supposed to start with a number in R, and 3 variables were written like that in our data set (1stFlrSF, 2ndFlrSF, 3SsnPorch)-thus generating a error message after-, we change the name of this 3 variables (to FstFlrSF, sndFlSF, TSsnPorch).
```{r cleaning data, echo=FALSE }
train <- train[,-1]

dput(names(train))
names(train) <- c("MSSubClass", "MSZoning", "LotFrontage", "LotArea", "Street", 
                  "Alley", "LotShape", "LandContour", "Utilities", "LotConfig", 
                  "LandSlope", "Neighborhood", "Condition1", "Condition2", "BldgType", 
                  "HouseStyle", "OverallQual", "OverallCond", "YearBuilt", "YearRemodAdd", 
                  "RoofStyle", "RoofMatl", "Exterior1st", "Exterior2nd", "MasVnrType", 
                  "MasVnrArea", "ExterQual", "ExterCond", "Foundation", "BsmtQual", 
                  "BsmtCond", "BsmtExposure", "BsmtFinType1", "BsmtFinSF1", "BsmtFinType2", 
                  "BsmtFinSF2", "BsmtUnfSF", "TotalBsmtSF", "Heating", "HeatingQC", 
                  "CentralAir", "Electrical", "FstFlrSF", "SndFlrSF", "LowQualFinSF", 
                  "GrLivArea", "BsmtFullBath", "BsmtHalfBath", "FullBath", "HalfBath", 
                  "BedroomAbvGr", "KitchenAbvGr", "KitchenQual", "TotRmsAbvGrd", 
                  "Functional", "Fireplaces", "FireplaceQu", "GarageType", "GarageYrBlt", 
                  "GarageFinish", "GarageCars", "GarageArea", "GarageQual", "GarageCond", 
                  "PavedDrive", "WoodDeckSF", "OpenPorchSF", "EnclosedPorch", "TSsnPorch", 
                  "ScreenPorch", "PoolArea", "PoolQC", "Fence", "MiscFeature", 
                  "MiscVal", "MoSold", "YrSold", "SaleType", "SaleCondition", "SalePrice")

```

After, we convert variables character into factor
```{r cleaning data 3}
train<- train%>%mutate_if(is.character,as.factor)
```

Then, we erase the missing values in our data set (as we saw in ChallengeA)
```{r cleaning data 4, echo=FALSE }
train %>% summarise_all(.funs = funs(sum(is.na(.)))) %>% gather(key = "feature", value = "missing.observations") %>% filter(missing.observations > 0)
remove.vars <- train %>% summarise_all(.funs = funs(sum(is.na(.)))) %>% gather(key = "feature", value = "missing.observations") %>% filter(missing.observations > 100) %>% select(feature) %>% unlist
train <- train %>% select(- one_of(remove.vars))
train %>% summarise_all(.funs = funs(sum(is.na(.)))) %>% gather(key = "feature", value = "missing.observations") %>% filter(missing.observations > 0)
train <- train %>% filter(is.na(GarageType) == FALSE, is.na(MasVnrType) == FALSE, is.na(BsmtFinType2) == FALSE, is.na(BsmtExposure) == FALSE, is.na(Electrical) == FALSE)
anyNA(train)
```

We did the randomforest regression on the train dataset
```{r randomforest reg }
RFreg<-randomForest(SalePrice ~ ., data = train, ntree=500, mtry=5, na.action=na.roughfix)
RFreg
summary(RFreg)
```


